WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-07-20 article/Article.tex
some addition to the article
darcs-hash:20060720100417-2fc9d-0aa458112b663188925cf08adb579590249e8d9b.gz

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.1}

@@

Note that ITK already has a wrapping infrastructure, and that WrapITK is based
on it, and use the same tools: CMake \cite{CMakeWebSite}, GCC-XML \cite{GccxmlWebsite}
and CableSwig\footnote{CableSwig is based on a now quite old version of SWIG
\cite{SwigWebSite}.} \cite{CableSwigWebSite}. This project aims to
address the following deficits of the existing wrappers (and others):
\begin{itemize}
  \item  ITK is a huge library, but only a small number of classes are available
in target languages. It become quickly frustrating for the user, especially when
he has to spend lot of time to extend the current set of classes. Even if it is
not yet complete, the WrapITK's set of classes have been highly extended. Moreover,
the user can choose at build time which types and which dimensions he want to wrap.
With 197 wrapped filters, WrapITK covers 62\% of the available filters.

@@

Several tests are available\footnote{There is currently 49 tests with the default
configuration.} for Python, Tcl and Java. They ensure the high quality of WrapITK.
They can be run with the \verb$ctest$ command.

\newpage
\part{Performance}

@@

For the user who don't want to use darcs \cite{DarcsWebSite} but still want the last development version,
a nightly updated archive is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz}.

@@

WrapITK will work properly with the ITK 2.8.0 release.

There are some optional
patches to the ITK source in \verb$WrapITK/patches/optional$ which can be applied to
version 2.6.0. These optional patches provide
better support for python by providing some methods like \verb$__str__$, or methods
for standard python sequence interface (see below).

@@

@@

We thank Andr\'e Bongers.

>>>>

% Increment the release number whenever significant changes are made.
% The author and/or editor can define 'significant' however they like.
\release{0.2}

@@

Note that ITK already has a wrapping infrastructure, and that WrapITK is based
on it, and use the same tools: CMake \cite{CMakeWebSite}, GCC-XML \cite{GccxmlWebsite}
and CableSwig\footnote{CableSwig is based on a now quite old version of SWIG
\cite{SwigWebSite}.} \cite{CableSwigWebSite}. This project aims to
address the following deficits of the existing wrappers (and others):
\begin{itemize}
  \item  ITK is a huge library, but only a small number of classes are available
in target languages. It become quickly frustrating for the user, especially when
he has to spend lot of time to extend the current set of classes. Even if it is
not yet complete, the WrapITK's set of classes have been highly extended. Moreover,
the user can choose at build time which types and which dimensions he want to wrap.
With 202 wrapped filters, WrapITK covers 63\% of the available filters.

@@

Several tests are available\footnote{There is currently 67 tests with the default
configuration.} for Python, Tcl and Java. They ensure the high quality of WrapITK.
They can be run with the \verb$ctest$ command.

\newpage
\part{Performance and memory usage}

WrapITK provides an interface to some C++ compiled code, and so, execution time
are very similar to pure C++ programs in most of cases.

The major difference comes from the memory
usage: while a C++ program will produce a binary executable containing only
the required code, WrapITK binary contains all the classes wrapped, and so
WrapITK can take a significant amount of memory.

Some comvenient features, like sequence management in python, can be quite
inefficient and should not be used in a loop.

@@

For the user who don't want to use darcs \cite{DarcsWebSite} but still want the last development version,
a nightly updated archive is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.tar.gz} or
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/WrapITK/WrapITK.zip}.

@@

WrapITK will work properly with the ITK 2.8.1 release.

There are some optional
patches to the ITK source in \verb$WrapITK/patches/optional$ which can be applied to
version 2.8.1. These optional patches provide
better support for python by providing some methods like \verb$__str__$, or methods
for standard python sequence interface (see below).

@@

\newpage
\part{Known bugs}
See \url{http://voxel.jouy.inra.fr/roundup/wrapitk/}.

@@

We thank Andr\'e Bongers for his help to debug java build on windows plateform.
